Point estimates comparison for the simplified Naomi model

### 2023-07-03 src/naomi-simple_point-estimates/point-estimates.Rmd
Add largest error data tables in point estimate notebook

>>>>

Where are the greatest errors occurring for the mean?

```{r}
df_plot_latent %>%
  filter(indicator == "Posterior mean estimate") %>%
  mutate(diff = abs(approximate - truth)) %>%
  arrange(desc(diff)) %>%
  select(indicator, par, id, method, truth, approximate, diff) %>%
  DT::datatable()
```

What about for the standard deviations?

```{r}
df_plot_latent %>%
  filter(indicator == "Posterior SD estimate") %>%
  mutate(diff = abs(approximate - truth)) %>%
  arrange(desc(diff)) %>%
  select(indicator, par, id, method, truth, approximate, diff) %>%
  DT::datatable()
```
